\documentclass[../booklet.tex]{subfiles}

\begin{document}

\section[Fuzzy Greedy Randomized Adaptive Search Procedure and Simulation Model to solve the Team Orienteering Problem with Time Windows. {\it Airam Expósito Márquez, Christopher Expósito Izquierdo, Belén Melian Batista and José Marcos Moreno Vega}]{Fuzzy Greedy Randomized Adaptive Search Procedure and Simulation Model to solve the Team Orienteering Problem with Time Windows}
\index[authors]{Márquez, Airam Expósito} \index[authors]{Izquierdo,  Christopher Expósito} \index[authors]{Batista,  Belén Melian} \index[authors]{Vega, José Marcos Moreno}

\begin{center}
  {\it Airam Expósito Márquez, Christopher Expósito Izquierdo, Belén Melian Batista and José Marcos Moreno Vega}
\end{center}
%\begin{minipage}{1\textwidth}
%\end{minipage}

\vskip 0.8cm


Tourism is a relevant economic activity that provides important resources (income, employment,...) to countries. When a tourist visits a country or city, he/she wants to know their points of interest. To do this, he/she must select some of the places according to his/her preferences and design routes to visit them. This problem can be adequately modeled as a Team Orienteering Problem with Time Windows (TOPTW). In this paper we propose a fuzzy GRASP and a multi-agent simulation model to solve the TOPTW. Our proposal incorporates two criteria to build the restricted candidate list. The computational results obtained show the validity of the proposal.
\keywords{Tourism  \and GRASP \and Fuzzy \and Simulation model.}



\end{document}
