\documentclass[../booklet.tex]{subfiles}

\begin{document}

\subsection[Combining Multi-Agent Systems and Subjective Logic to Develop Decision Support Systems. {\it Cesar Gonzalez Fernandez, Javier Cabezas Givica, Alberto Fernandez and Isaac Martin de Diego}]{Combining Multi-Agent Systems and Subjective Logic to Develop Decision Support Systems}
\index[authors]{Fernandez, Cesar Gonzalez} \index[authors]{Givica,  Javier Cabezas} \index[authors]{Fernandez,  Alberto} \index[authors]{Diego, Isaac Martin de}

\begin{center}
  {\it Cesar Gonzalez Fernandez, Javier Cabezas Givica, Alberto Fernandez and Isaac Martin de Diego}
\end{center}
%\begin{minipage}{1\textwidth}
%\end{minipage}

\vskip 0.8cm

Nowadays, the rise of the interconnected computer networks and the increase of processed data have led to producing distributed systems. These systems usually separate multiple tasks into other simpler with the goal of maintaining efficiency. This paradigm has been observed for a long time in different animal organisations as insect colonies and fish shoals. For this reason, distributed systems that emulate the biological rules that govern their collective behaviour have been developed. \emph{Multi-Agent Systems} (MAS) have shown their ability to address this issue. This paper proposes \emph{Ant Colony based Architecture with Subjective Logic} (ACA-SL). It is a bio-inspired model based on ant colony structures. It makes use of MAS to distribute tasks and \emph{Subjective Logic} (SL) to produce \emph{Decision Support Systems} (DSS) according to the combination of individual opinions. A system implementation based on the proposed architecture has been generated to illustrate the viability of the proposal. The proposed architecture is intended to be the starting point for developing systems that solve a variety of problems.

\keywords{Multi-agent system \and Subjective logic \and Bio-inspired system \and Distributed organisation \and Decision Support system}



\end{document}
